Assignment 2

### 2019-09-01 ex2/paper/paper.tex

%%
%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf,nonacm]{acmart}

\usepackage{multirow}

\settopmatter{printacmref=false} % Removes citation information below abstract
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column

@@

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Alexander Hartl (e01125115)}
\authornote{Both authors contributed equally to this research.}
%\email{alexander.hartl@tuwien.ac.at}

\author{Maximilian Bachl (e01100143)}
%\authornote[1]{Both authors contributed equally to this research.}
\authornotemark[1]
%\email{maximilian.bachl@gmail.com}

@@

\begin{figure*}[p]
\includegraphics[width=0.48\textwidth]{../ice/sourceTransportPort_nn_0.pdf}
\includegraphics[width=0.48\textwidth]{../ice/sourceTransportPort_rf_0.pdf}

\includegraphics[width=0.48\textwidth]{../ice/apply(mean(ipTTL),forward)_nn_0.pdf}
\includegraphics[width=0.48\textwidth]{../ice/apply(mean(ipTTL),forward)_rf_0.pdf}

\includegraphics[width=0.48\textwidth]{../ice/apply(stdev(ipTotalLength),forward)_nn_0.pdf}
\includegraphics[width=0.48\textwidth]{../ice/apply(stdev(ipTotalLength),forward)_rf_0.pdf}

>>>>

%%
%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[10pt,sigconf,letterpaper]{acmart}
\acmYear{2019}
\copyrightyear{2019}
\acmConference{CoNEXT '19}{December 9-12, 2019}{Orlando, Florida, USA}

\usepackage{multirow}
\usepackage{blindtext}

%\settopmatter{printacmref=false} % Removes citation information below abstract
%\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column

@@

\begin{abstract}
    \blindtext
\end{abstract}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Maximilian Bachl}
\affiliation{\institution{Technische Universität Wien}}
%\authornote{Both authors contributed equally to this research.}
\email{maximilian.bachl@tuwien.ac.at}

\author{Alexander Hartl}
\affiliation{\institution{Technische Universität Wien}}
%\authornotemark[1]
\email{alexander.hartl@tuwien.ac.at}

\author{Tanja Zseby}
\affiliation{\institution{Technische Universität Wien}}
\email{tanja.zseby@tuwien.ac.at}

\author{Joachim Fabini}
\affiliation{\institution{Technische Universität Wien}}
\email{joachim.fabini@tuwien.ac.at}

@@

\begin{figure*}[p]
\includegraphics[width=0.48\textwidth]{../ice/sourceTransportPort_nn.pdf}
\includegraphics[width=0.48\textwidth]{../ice/sourceTransportPort_rf.pdf}

\includegraphics[width=0.48\textwidth]{../ice/apply(mean(ipTTL),forward)_nn.pdf}
\includegraphics[width=0.48\textwidth]{../ice/apply(mean(ipTTL),forward)_rf.pdf}

\includegraphics[width=0.48\textwidth]{../ice/apply(stdev(ipTotalLength),forward)_nn.pdf}
\includegraphics[width=0.48\textwidth]{../ice/apply(stdev(ipTotalLength),forward)_rf.pdf}
